TacticToe: Learning to Prove with Tactics

### 2018-03-21 tactictoe_jv.tex
section 1.3

The different components depicted in Fig~\ref{fig:components} give a 
high-level overview of the techniques necessary to generate 
tactic-level proofs by learning from recorded knowledge. From a formal library 
of ITP proofs, we extract and record tactic invocations 
in Section~\ref{sec:recording}. Based on such training examples, we
  build efficient machine learning classifiers in Section~\ref{s:prediction}. 
  At the basis of those predictions are 
  similarity measures computed from syntactic features of mathematical formulas 
  .
  Modification of the knowledge base performed by orthogonalization 
  in Section~\ref{sec:ortho} and abstraction in Section~\ref{sec:synthesis}
  improves the quality of the databases.
  And the preselection method described in Section~\ref{sec:presel} increases 
  the speed 
  of the prediction algorithm.
  The learned predictors relying on this knowledge serves as
  guidance for the proof search algorithm presented in 
  Section~\ref{sec:proofsearch} 
  which explores different proof paths in the proof tree defined in 
  Section~\ref{sec:prelim}. 
  The result, if
  successful, is a verified human-level proof composed of \holfour
  tactics minimized in Section~\ref{sec:proofdisplay}. And in 
  Section~\ref{s:experiments}, we evaluate the system 
  on a large set of theorems originating from \holfour.
  The generated proofs are compared with human proofs in 
  Section~\ref{sec:case_study}.

The section order does not follow the implementation. In this way, 
we can give a description of the proof search algorithm sooner. This order is 
beneficial for the reader as it shows the essential for our work before 
technical details on the prediction and recording algorithms.

>>>>

The different components depicted in Fig~\ref{fig:components} give a 
high-level overview of the techniques necessary to generate 
tactic-level proofs by learning from recorded knowledge. From a formal library 
of ITP proofs, we extract and record tactic invocations 
in Section~\ref{sec:recording}. Based on such training examples, we
  build efficient machine learning classifiers in Section~\ref{s:prediction}.
  Modification of the knowledge base, shown as the training loop in 
  Fig~\ref{fig:components} and
  achieved by orthogonalization in Section~\ref{sec:ortho} and completed by 
  an abstraction technique in Section~\ref{sec:synthesis},
  improves the quality of the predictions.
  And the preselection method described in Section~\ref{sec:presel} increases 
  the speed of the prediction algorithm.
  The learned predictors relying on this knowledge guide the proof search 
  algorithm presented in Section~\ref{sec:proofsearch}.
  The search algorithm explores different proof paths in the proof tree which 
  is defined in Section~\ref{sec:prelim}. 
  The result, if
  successful, is a verified human-level proof composed of \holfour
  tactics minimized in Section~\ref{sec:proofdisplay}. And in 
  Section~\ref{s:experiments}, we evaluate the system 
  on a large set of theorems originating from \holfour.
  The generated proofs are compared with human proofs in 
  Section~\ref{sec:case_study}.

The section order does not follow the implementation to give a description of 
the proof search algorithm sooner. This order is 
beneficial for the reader as it shows the essential of our work before 
technical details on the prediction and recording algorithms.
